### 2016-05-27 R/ITHIM.Rmd
Introduced AF to script

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
library("ggplot2")
library("reshape2")
library("plyr")
```
```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE}
library("devtools")
install_github("syounkin/ITHIM")
library("ITHIM")
date()
```

@@

RR <- createActiveTransportRRs()
RR <- matrix(RR$BreastCancer[,"F"],nrow=nAgeClass,ncol = 5, byrow = FALSE)

@@

RR^(totalMETs$F^0.5)

```{r ITHIM}
names(ITHIM)
```

>>>>

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
library("ggplot2")
library("reshape2")
library("plyr")
```
```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE}
library("devtools")
install_github("syounkin/ITHIM", ref = "devel", force = TRUE)
library("ITHIM")
date()
```

@@

RR <- createActiveTransportRRs()

nAgeClass <- 8

@@

totalMETs.baseline <- lapply(totalMETs.baseline, function(x) ifelse(x<2.5,0.1,x))
totalMETs.scenario <- lapply(totalMETs.scenario, function(x) ifelse(x<2.5,0.1,x))

## RR for Females and Breast Cancer
RR <- matrix(RR$BreastCancer[,"F"],nrow=nAgeClass,ncol = 5, byrow = FALSE)
RR.baseline <- RR^(totalMETs.baseline$F^0.5)
RR.scenario <- RR^(totalMETs.scenario$F^0.5)
diseaseBurden <- RR.baseline/RR.scenario
burden <- 1 - (rowSums(diseaseBurden)-ncol(diseaseBurden))/rowSums(diseaseBurden)
(AF <- 1 - burden)
```

```{r ITHIM}
ITHIM <- ITHIM.baseline
names(ITHIM)
```
